Evolution of the AGN UV luminosity function from redshift 7.5

### 2018-02-22 Paper/paper.tex
Update

\documentclass[a4paper,fleqn,usenatbib]{mnras}
\usepackage[T1]{fontenc}
\usepackage{ae,aecompl}
\usepackage{graphicx}	
\usepackage{amsmath}	
\usepackage{amssymb}
\usepackage{pdflscape}
\usepackage{siunitx}
\def\lya{Ly$\alpha$~}
\usepackage{color}
\definecolor{notecolor}{rgb}{0.8,0,0}
\newcommand{\gk}[1]{{\bf \color{notecolor} [#1]}}

@@

@@

Our derivation of the LyC emissivity of AGN allows us to see if the
corresponding hydrogen photoionization rate is consistent with the
measured CDDF of the low-redshift ($z<0.5$) Ly$\alpha$ forest
\citep{2016ApJ...817..111D}.  \citet{2014ApJ...789L..32K} argued that
in order to match the CDDF observed by \citet{2016ApJ...817..111D} at
% Define acronym CDDF.
these redshifts, hydrodynamical cosmological simulations require a
hydrogen photoionization rate that is a factor of five larger than
that in the UV background (UVB) model of \citet{2012ApJ...746..125H}.
% This factor looks more than five in our plot!
Several recent studies in the literature have addressed this ``photon
underproduction crisis''.  On the one hand, these studies emphasised
the uncertainty in the \citet{2012ApJ...746..125H} UVB model at these
redshifts due to the lack of certainty in the UV photon emissivities
of galaxies and AGN \citep{2015MNRAS.451L..30K, 2015ApJ...811....3S}.
On the other hand, they noted the uncertainty in the results of the
cosmological simulations at these redshifts, due to effects such as
AGN feedback and limited numerical resolution
\citep{2015ApJ...811....3S, 2017MNRAS.467L..86V, 2017MNRAS.471.1056N,
  2017ApJ...837..106O, 2017MNRAS.466..838G, 2017MNRAS.467.3172G,
  2017ApJ...835..175G}.  A general conclusion of these studies was
that the discrepancy between the photoionization rate required by the
observed CDDF and predicted by the UVB model of
\citet{2012ApJ...746..125H} is likely to be smaller than that found by
\citet{2014ApJ...789L..32K}.  The discrepancy is about a factor of 2
instead of 5.

@@

% Add an appendix on comparison with Giallongo.

>>>>

\documentclass[a4paper,fleqn,usenatbib]{mnras}
\usepackage[T1]{fontenc}
\usepackage{ae,aecompl}
\usepackage{graphicx}	
\usepackage{amsmath}	
\usepackage{amssymb}
\usepackage{pdflscape}
\usepackage{siunitx}
\def\lya{Ly$\alpha$~}
\usepackage{color}
\definecolor{notecolor}{rgb}{0.8,0,0}
\newcommand{\gk}[1]{{\bf \color{notecolor} [#1]}}
\def\HI{\hbox{H~$\scriptstyle\rm I$}}
\def\HII{\hbox{H~$\scriptstyle\rm II$}}
\def\nHI{{\rm HI}}
\def\nH{{\rm H}}
\def\nHII{{\rm HII}}
\def\nHe{{\rm He}}
\def\nHeI{{\rm HeI}}
\def\nHeII{{\rm HeII}}
\def\nHeIII{{\rm HeIII}}
\def\bHII{\hbox{\bf H~$\scriptstyle\bf II$}}
\def\HeI{\hbox{He~$\scriptstyle\rm I$}}
\def\HeII{\hbox{He~$\scriptstyle\rm II$}}
\def\HeIII{\hbox{He~$\scriptstyle\rm III$}}
\def\bHeII{\hbox{\bf He~$\scriptstyle\bf II$}}
\def\HeIII{\hbox{He~$\scriptstyle\rm III$}}

@@

We now consider the implications for hydrogen and helium reionization
for the ionizing photon emissivity derived above.  This requires that
we extrapolate the emissivity of Equation XX to higher redshifts.
Unfortunately, the volume emissivity in our model cannot be
extrapolated to higher redshifts.  The model of Hopkins suffered with
the same problem.  \gk{Do we need to show two cases here?  One in
  which we extrapolate the emissivity and another in which we stop
  where data end.  There is perhaps a third possibility in which use
  the current emissivity model upto where data end.}  The evolution of
the volume averaged ionized fraction of hydrogen is given by
\citep{2012ApJ...746..125H}
\begin{equation}
{dQ_\nHII\over dt}={\dot n_{\rm ion}\over \langle n_\nH \rangle} -{Q_\nHII\over
\langle t_{\rm rec}\rangle},
\label{eq:qdot}
\end{equation}
and the corresponding equation doubly ionized Helium is
\begin{equation}
{dQ_\nHeIII\over dt}={\dot n_{\rm ion,4}\over \langle n_\nHe \rangle} -{Q_\nHeIII\over
\langle t_{\rm rec,He}\rangle}.
\label{eq:qHedot}
\end{equation}
We assume that the Helium is singly reionized together with hydrogen.
In order to get the 4~Ry emissivity of quasars we use the SED from
equation XX.  The recombination times are given by
\begin{equation}
\langle t_{\rm rec}\rangle=[\chi \langle n\rangle \alpha_B\,C]^{-1},
\label{eq:trec}
\end{equation}
where $n$ is the volume averaged density of hydrogen and helium,
respectively.  We assume that hydrogen and helium have similar
clumping factors, given by \citep{2015ApJ...813L...8M}
\begin{equation}
  C = 2.8\left(\frac{1+z}{6}\right)^{-1.1}.
\end{equation}
For the helium recombination coeffienct, we use the fitting function
provided by \citet{1997MNRAS.292...27H}.  For hydrogen recombination
coefficient, we use the fitting function provided by
\citet{2011piim.book.....D}.

The resultant reionization histories of hydrogen and helium are shown
in Figure XX.  We also show the reionization histories from
\citep{2012ApJ...746..125H} and \citep{2015ApJ...813L...8M} for
comparison.  As expected from the emissivity result of the previous
section, quasars cannot single handedly reionize hydrogen.  However
they can reionise \HeII.  The Helium reionization completes at
redshift $z=3.5$--$3.7$ depending on the luminosity down to which you
integrate the quasar luminosity function.  This is consistent with the
Helium \lya opacity measurements of \citet{2016ApJ...825..144W}.

@@

Our derivation of the LyC emissivity of AGN allows us to see if the
corresponding hydrogen photoionization rate is consistent with the
measured CDDF of the low-redshift ($z<0.5$) Ly$\alpha$ forest
\citep{2016ApJ...817..111D}.  \citet{2014ApJ...789L..32K} argued that
in order to match the CDDF observed by \citet{2016ApJ...817..111D} at
\gk{Define acronym CDDF.}  these redshifts, hydrodynamical
cosmological simulations require a hydrogen photoionization rate that
is a factor of five larger than that in the UV background (UVB) model
of \citet{2012ApJ...746..125H}.  \gk{This factor looks more than five
  in our plot!}  Several recent studies in the literature have
addressed this ``photon underproduction crisis''.  On the one hand,
these studies emphasised the uncertainty in the
\citet{2012ApJ...746..125H} UVB model at these redshifts due to the
lack of certainty in the UV photon emissivities of galaxies and AGN
\citep{2015MNRAS.451L..30K, 2015ApJ...811....3S}.  On the other hand,
they noted the uncertainty in the results of the cosmological
simulations at these redshifts, due to effects such as AGN feedback
and limited numerical resolution \citep{2015ApJ...811....3S,
  2017MNRAS.467L..86V, 2017MNRAS.471.1056N, 2017ApJ...837..106O,
  2017MNRAS.466..838G, 2017MNRAS.467.3172G, 2017ApJ...835..175G}.  A
general conclusion of these studies was that the discrepancy between
the photoionization rate required by the observed CDDF and predicted
by the UVB model of \citet{2012ApJ...746..125H} is likely to be
smaller than that found by \citet{2014ApJ...789L..32K}.  The
discrepancy is about a factor of 2 instead of 5.

@@

\appendix

\section{Comparison with Giallongo sample}
\label{sec:conv}

In our analysis above, we did not include the 22 low-luminosity
($M_{1450}>-22.6$) AGN between redshifts $z=4.1$ and $6.3$ reported by
\citet{2015AA...578A..83G} using a novel X-ray/NIR selection
criterion.  This was because we wanted to restrict our sample to
quasars that have robust spectroscopic redshift determinations.  In
their work, \citet{2015AA...578A..83G} found a steep faint-end of the
luminosity function at these redshifts.  With this luminosity function
they obtained a large value of hydrogen ionizing emissivity that could
explain the \lya data singlehandedly.  In this section, we compare our
results with \citet{2015AA...578A..83G}.  The black points in Figure
XX show the parameters of the double power law luminosity function
when the \citet{2015AA...578A..83G} sample is added to our analysis.
The parameter values do not change significantly.  The
\citet{2015AA...578A..83G} sample is thus consistent with the double
power law luminosity function preferred by other data at comparable
redshifts.  However, as we see in Figure XX, the total emissivity in
our model is still significantly lower than that obtained by
\citet{2015AA...578A..83G}.  Figure XX provides an explanation for
this. The double power law fits favoured by \citet{2015AA...578A..83G}
are quite different from our fits.  The character luminosity $M_*$
favoured by \citet{2015AA...578A..83G} is much fainter ($\sim -23$ at
$z = 5$) than that resulting out of our analysis ($\sim -29$ at $z =
5$).  Figure XX suggests that this is because of the SDSS Stripe 82
data \gk{citation} and because \citet{2015AA...578A..83G} ignore the
Kashikawa and Willott samples \gk{citation}.  It is possible that our
corrections to the Glikman data \gk{citation} also plays a role in
this.  In sum, the differnce in our emissivities is not due to lack of
faint quasars but because of the difference with Giallongo at
intermediate luminosities.
